Taking Dyads Seriously

### 2018-03-16 paper/5_concl.tex
some changes to concl

Three basic approaches have appeared as alternatives in the literature.\footnote{A good overview may be found in \cite{stewart:2014}, which proposes a variational estimation approach to latent network models.}
None of these approaches has as yet been widely employed nor even cited in the substantive literature, and each is mainly known inside of the network methodology community.  We discuss each of these approaches and briefly compare them to the AME approach.

@@

This approach focuses on the standard errors, needed for significance testing, but ignores the bias introduced into the regression coefficients, as discussed above.  Nor does it provide any way to access the higher-order network effects. It simply provides a fix to the estimated standard errors.  One of the main problems with dependent data, is that it takes more data to calculate basic quantities accurately. This is true even for a simple t-test \citep{ward:gleditsch:2008}.

However, more generally how does cluster-robust vriance estimation perform compared for example to AME?  XYZ.

@@

However, how does Poast's approach compare to AME?  XX, YY, ZZ.

%see also Poast, Paul. ``Dyads are Dead, Long Live Dyads: The Limits (but not Rejection) of Dyadic Designs in International #Relations Research.'' International Studies Quarterly. June 2016: 369-374
%and
%Fordham, Benjamin and Poast, Paul. ``All Alliances are Multilateral: Rethinking Alliance Formation in the International #System.'' Journal of Conflict Resolution. August 2016: 840-865.
%but note: Below are files for replicating or extending results in the paper ``All Alliances are Multilateral'' (w/ Benjamin #Fordham). We thank Daina Chiba (Essex), whose effort to replicate our work uncovered the difficulties scholars face (myself #included!) when creating k-adic data and, therefore, led to this webpage as a help to future scholarship.
% also used by Brandon Kinne

%maybe used by Peaceful Uncertainty: When Power Shocks Do Not Create Commitment Problems
%Muhammet A Bas  Robert Schub ISQ 2017

@@

\citet{erikson:etal:2014} base their approach on MRQAP developed by Krackhardt (1988), \nocite{krackhart:1988} an approach from network studies that draws upon the fact that networks have repeated observations, which induces some correlation of observations that in turn lead to bias in standard errors of general linear models of these data. MRQAP randomly permutes the rows and columns of the data, creating multiple datasets which are then each analyzed in the standard way to generate a sampling distribution of all possible (but not observed) networks from the observed data. Herein, the data are randomly permuted on the assumption that the errors are exchangeable.  Many permutations are created and models are run on all of them, then the distributions of tests statistics (not parameters) are examined. They find in their reanalysis that ``the randomization results show that conventional t-tests are inappropriate for
testing hypotheses on dyad-year data because they rely on highly overconfident standard errors'' (page 462).  This shows that in dyadic data analysis with general linear models, especially with hundreds of thousands of observations, the standard t-test is polyannaish in finding significant relations.  One simple fix is MRQAP, which address---again---the standard errors. But this approach doesn't really get at the underlying data generating process, and is based on an approach to modeling dependent data that is known to produce bias and ignore dependencies.  It is a fix of a leaky window, when the roof is collapsed. (okay, too much, but hey.)

How does MRQAP compare to AME?  XXX, YYY, ZZZ

>>>>

Three basic approaches have appeared as alternatives in the literature.\footnote{A good overview may be found in \cite{stewart:2014}, which proposes a variational estimation approach to latent network models.}
None of these approaches has as yet been widely employed nor even cited in the substantive literature, and each is mainly known inside of the network methodology community.  We discuss each of these approaches and briefly compare them to the AME approach. The takeaway is that the AME approach enables users to more accurately conduct inference on dependent data than these other approaches which have been proposed.

@@

This approach focuses on the standard errors, needed for significance testing, but ignores the bias introduced into the regression coefficients, as discussed above.  Nor does it provide any way to access the higher-order network effects, a point that Aronow et alia make in their article, noting that it is only targeted at dyadic (not higher level) dependencies. This approach simply provides a fix to the estimated standard errors.  
%One of the main problems with dependent data is that it takes more data to calculate basic quantities accurately. This is true even for a simple t-test \citep{ward:gleditsch:2008}.

Thus, cluster-robust vriance estimation is not designed to answer the same questions as AME.  As shown in the original article, it does provide a way to  estimate standard errors (in a sitution with only dyadic dependence) that substantially improves over the standard logistic regression approach.  However, it ignores the higher-order dependencies which are the focus of the AME model.

@@

However, how does Poast's approach compare to AME? We found in simulations structured like those reported herein run with the k-adic model that the k-adic model was not able to improve over AME, and in fact were dramatically worse at recovering the real data generating process than AME models.

@@

\citet{erikson:etal:2014} base their approach on MRQAP developed by Krackhardt (1988), \nocite{krackhart:1988} an approach from network studies that draws upon the fact that networks have repeated observations, which induces some correlation of observations that in turn lead to bias in standard errors of general linear models of these data. MRQAP randomly permutes the rows and columns of the data, creating multiple datasets which are then each analyzed in the standard way to generate a sampling distribution of all possible (but not observed) networks from the observed data. Herein, the data are randomly permuted on the assumption that the errors are exchangeable.  Many permutations are created and models are run on all of them, then the distributions of tests statistics (not parameters) are examined. They find in their reanalysis that ``the randomization results show that conventional t-tests are inappropriate for
testing hypotheses on dyad-year data because they rely on highly overconfident standard errors'' (page 462).  This shows that in dyadic data analysis with general linear models, especially with hundreds of thousands of observations, the standard t-test is polyannaish in finding significant relations.  One simple fix is MRQAP, which addresses---again---the standard errors. But this approach doesn't really get at the underlying data generating process, and is based on an approach to modeling dependent data that is known to produce bias and ignore dependencies.  In our simulations when applied to a MRQAP model, we find that it does not recover the data generating process as well as AME. This is quite due in part to the fact that it treats the dependencies as nuisance to be eliminated rather than focused on explicitly as with AME.
